%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Back‑end developer} % Affiliation/role
    {Context free automata simulator} % Organization/group
    {Belgium} % Location
    {Sep. 2022 ‑ Mar. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Implemented Context free automata and grammer simulator + Conversion (to CNF)}
      \end{cvitems}
    }
  
%---------------------------------------------------------

  \cventry
    {Back‑end developer} % Affiliation/role
    {Secure communication protocols} % Organization/group
    {Belgium} % Location
    {Sep. 2023 ‑ Jan. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed and implemented various cryptographic solutions including AES, Salsa20, RSA (with OAEP and Rabin-Miller primality), and MAC using SHA1/HMAC-SHA512}
        \item {Ensured secure communication through encryption, key exchange protocols, and defenses against attacks like MitM and replay, while configuring servers for decryption, authentication, and message integrity.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Full‑Stack developer} % Affiliation/role
    {News aggregator} % Organization/group
    {Belgium} % Location
    {Sep. 2022 ‑ Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed a comprehensive news aggregator platform, integrating backend services with a dynamic front‑end interface}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Full‑stack Developer} % Affiliation/role
    {Digital city twin} % Organization/group
    {Belgium} % Location
    {Sep. 2023 ‑ May 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Played part the development of a Digital City Twin platform, enabling users to create and simulate digital twins of cities for urban planning and analysis}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
  {Developer} % Affiliation/role
  {Microservices Event manager} % Organization/group
  {Belgium} % Location
  {Apr. 2024 ‑ May 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Developed a Flask-based event management frontend with user authentication and calendar features, alongside a modular FastAPI backend API, and configured PostgreSQL for database schema creation.}
    \end{cvitems}
  }

%---------------------------------------------------------

  \cventry
    {Software developer} % Affiliation/role
    {Markov Chain text generator} % Organization/group
    {Belgium} % Location
    {Sep. 2022 ‑ Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {A text generator based on Markov chains, capable of generating text based on a given input text.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Developer} % Affiliation/role
    {ASL Detection} % Organization/group
    {Belgium} % Location
    {Jan. 2024 ‑ May 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Implemented two models for sign language recognition (pixel values and landmarks), with a GUI for real-time hand tracking using MediaPipe and OpenCV, in collaboration with Jason Liu and Orfeo Terkuci.}
      \end{cvitems}
    }

%---------------------------------------------------------


\end{cventries}
